---
title: "Subvastus cohort analysis"
author: "Corey Scholes"
affiliation: "EBM Analytics"
version: 1.0
type: "website"
number-sections: true
number-depth: 3
date: "2026-Mar-10"
date-modified: "2026-Mar-10"

bibliography: AORAGov references.bib

editor:
  visual
format:
  html:
    toc: true
    number-sections: true
    code-fold: true
    link-external-newwindow: true
    link-external-icon: true
    
    format:
  docx:
    toc: true
    number-sections: true

    
execute: 
  echo: false
  warning: false
  message: false
---

# Preamble

The following analysis is a report on the activity, quality and data contained in the AORA registry.

```{r}
#| label: load-packages

if (!require("pacman")) install.packages("pacman")
pacman::p_load(# Load required packages
  "patchwork",
  "nnet",
  "mgcv",
  "ggforce",
  "ggdag",
  "ggmap",
  "ggsurvfit",
  "geosphere",
  "dplyr",
  "flextable",
  "litedown",
  "grateful",
  "modelsummary",
  "quantreg",
  "readr",
  "knitr",
  "cardx",
  "forcats",
  "gargle",
  "googledrive",
  "googlesheets4",
  "openxlsx2",
  "tidyverse",
  "tidymodels",
  "lubridate",
  "consort",
  "gt",
  "gtsummary",
  "survival",
  "ggplot2",
  "ggdist",
  "ggfortify",
  "mice",
  "marginaleffects",
  "naniar",
  "quantreg",
  "broom",
  "epoxy",
  "broom.helpers",
  "stringr"
  )
  
  
```

Access to the AORA datasets was pre-authorised.

```{r}
#| label: auth2
#| echo: false

options(
  gargle_oauth_cache = ".secrets",
  gargle_oauth_email = TRUE
)

googledrive::drive_auth(
  cache = ".secrets", 
  email = TRUE
  )
```

A function was generated to retrieve files to call on later in the analysis for processing data imports.

```{r}
#| label: folder
#| echo: false

base_folder_id1 <- "10ThtWn4-IIOuTYPbNrhJkL6yBuPQjk5S"



```

```{r}
get_specific_snapshot <- function(folder_name, base_folder_id = base_folder_id1) {
  tryCatch({
    # Check if the folder exists in the base directory
    folder <- googledrive::drive_ls(as_id(base_folder_id), pattern = paste0("^", folder_name, "$"))
    
    if(nrow(folder) == 0) {
      stop(paste("Folder", folder_name, "not found"))
    }
    
    # Find the snapshot file in the specified folder
    snapshot_file <- googledrive::drive_ls(
      folder$id, 
      pattern = "Registry data snapshot\\.xlsx$"
    )
    
    if(nrow(snapshot_file) == 0) {
      stop("No snapshot file found in specified folder")
    }
    
    # Return both pieces of information as a list
    return(list(
      snapshot = snapshot_file,
      folder_name = folder$name
    ))
    
  }, error = function(e) {
    stop(paste("Error finding specified snapshot:", e$message))
  })
}
```

Data was retrieved from live database tables. Source files were specified and stored as global variables to call on in further functions.

```{r}
#| label: live-table
#| echo: false

SheetIDs <- list(
DbSS = "https://docs.google.com/spreadsheets/d/1fhW1LJbsdvkA7u-z1IGgI2qHwiOWXP6RMRH8-cgPXU8/edit",
IntHistory = "https://docs.google.com/spreadsheets/d/1YBYcxJtRIoH0rD87bWCBvIFiKQp-b-JmklWPOh_-wDY/edit"
)

# Treatments Masterlist - Timestamp is > Registry Start date (gsuite)

```

```{r}
#| label: read-tables

# Authenticate for sheets using the same token
gs4_auth(token = drive_token())



# ComplicTable <- googlesheets4::read_sheet(
#   ss = SheetIDs$DbSS,
#   sheet = "Complications",
#   col_names = TRUE,
#   col_types = "TccDccDc"
#   )
# 
# 
# #To match to acctData
# PatientTable <- googlesheets4::range_read(
#   ss = SheetIDs$DbSS,
#   sheet = "Patient",
#   range = "A7:P",
#   col_names = FALSE,
#   col_types = "DccccDcccDciccci"
#   )
# 
# 
# Patient_Col <- c(
#   "PatientCreationDate",
#   "PatientID",
#   "LastName",
#   "FirstName",
#   "AlternateID",
#   "DateOfBirth",
#   "Sex",
#   "RegistryStatus",
#   "RegistryStatusNotes",
#   "DateRegistryStatus",
#   "NotificationMethod",
#   "NoTreatmentRecords",
#   "Email",
#   "Phone",
#   "PostCode",
#   "TrueNoTreatments"
# )
# 
# colnames(PatientTable) <- Patient_Col
# 
# 
# MonitorPlan <- googlesheets4::range_read(
#   ss = SheetIDs$DbSS,
#   sheet = "Monitor Module",
#   range = "A1:O",
#   col_names = TRUE,
#   col_types = "ccccDTtincTccii"
#   )
# 
# 
# MonitorLog <- googlesheets4::range_read(
#   ss = SheetIDs$DbSS,
#   sheet = "MonitorModuleLog",
#   range = "A1:K",
#   col_names = TRUE,
#   col_types = "Tcicccccccc"
#   )
# 
# MonitorResponse <- googlesheets4::range_read(
#   ss = SheetIDs$DbSS,
#   sheet = "Monitoring",
#   range = "A1:Q",
#   col_names = TRUE,
#   col_types = "TccccccccccnccDic"
#   )
# 
# colnames(MonitorResponse) <- c(
#   "TimeStamp",
#   "Issues",
#   "IssueDescription",
#   "ProviderConsult",
#   "RatingRecovery",
#   "RatingPainControl",
#   "WorstPain24",
#   "Painkillers",
#   "NSAIDs",
#   "PainkillersOther",
#   "OtherDescription",
#   "WalkDistance",
#   "FormID",
#   "TreatmentID",
#   "TreatmentDate",
#   "DaysAfterSurgery",
#   "TreatmentIDDays"
# )
# 
# IntHistory <- googlesheets4::range_read(
#   ss = SheetIDs$IntHistory,
#   sheet = "AORA - Medical History_RawData", 
#   range = "A4:CO",
#   col_names = FALSE
#   )
# 
# IntHistoryCol <- googlesheets4::range_read(
#   ss = SheetIDs$IntHistory,
#   sheet = "AORA - Medical History_RawData", 
#   range = "A3:CO3",
#   col_names = FALSE
#   )
# 
#  colnames(IntHistory) <- IntHistoryCol
 
TreatTable <- googlesheets4::range_read(
  ss = SheetIDs$DbSS,
  sheet = "Treatment", 
  range = "A7:Z",
  col_names = FALSE
  )

TreatTableCol <- googlesheets4::range_read(
  ss = SheetIDs$DbSS,
  sheet = "Treatment", 
  range = "A1:Z1",
  col_names = FALSE
  )

 colnames(TreatTable) <- TreatTableCol
 
 

```

## Retrieve MMM

```{r}

# ── 1. Download the POA 2021 × MMM 2023 concordance ──────────────────────────
# Direct xlsx from data.gov.au (Dept of Health and Aged Care, CC BY 2.5 AU)
# https://www.data.gov.au/data/dataset/postal-areas-2021-by-modified-monash-model-2023
 
mmm_url <- "https://data.gov.au/data/dataset/9c4e8fab-e9c3-4728-80a8-e59643f258a5/resource/04ed31ba-d48b-437c-9279-f4b788b9dd90/download/poa_21-mmm_23.xlsx"

tmp <- tempfile(fileext = ".xlsx")
download.file(mmm_url, destfile = tmp, mode = "wb")

 concordance_raw <- openxlsx2::wb_to_df(tmp, start_row = 8, start_col = 2, skip_empty_cols = TRUE)

# ── 2. Inspect and clean the concordance ─────────────────────────────────────
# Preview structure first — column names may vary; check with:
 glimpse(concordance_raw)

MMMPostcode <- concordance_raw |>
  rename_with(str_to_lower) |>
  rename(
    postcode  = "poa 2021 code",
    mmm_code  = "mmm 2023"
  ) |>
  summarise(
    mmm_code       = max(mmm_code, na.rm = TRUE),
    mmm_ambiguous  = n() > 1,
    .by = postcode
  )  |>
  mutate(
    postcode = as.character(postcode),
    mmm_code = as.integer(mmm_code),
    mmm_label = case_when(
      mmm_code == 1 ~ "Metropolitan",
      mmm_code == 2 ~ "Regional centre",
      mmm_code == 3 ~ "Large rural town",
      mmm_code == 4 ~ "Medium rural town",
      mmm_code == 5 ~ "Small rural town",
      mmm_code == 6 ~ "Remote community",
      mmm_code == 7 ~ "Very remote community",
      .default      = NA_character_
    )
  ) |>
  select(postcode, mmm_code, mmm_label, mmm_ambiguous)

```

```{r}


IntHistory1 <- IntHistory |> dplyr::select(
  FormIDMedicalHistory,
  EducationLevel,
  SmokingStatus,
  AlcoholConsumption,
  ActivityDuration,
  SymptomOnset,
  SymptomDuration
) |> rename(
  FormID = "FormIDMedicalHistory"
) |> distinct(
  FormID,
  .keep_all = TRUE
  ) |> mutate(
    TreatmentID = str_extract(FormID, "^\\d+\\.\\d+"),
    SymptomDuration1 = if_else(
      as.numeric(str_extract(SymptomDuration, "\\d+")) >1000,
      NA,
      as.numeric(str_extract(SymptomDuration, "\\d+"))
  )) 

```

```{r}

KneeIntraop <- googlesheets4::range_read(
  ss = SheetIDs$DbSS,
  sheet = "Knee Arthritis Treatments", 
  range = "A2:X",
  col_names = TRUE, 
  col_types = "Tccccccccccccccccccccncc"
  )
```

A static registry snapshot was retrieved and formatted based on the fixed date of preparation of the snapshot (01-Dec-2025).

```{r}

# Authenticate for sheets using the same token
gs4_auth(token = drive_token())

# To get a snapshot from a specific folder (e.g., "20230415")
specific_snapshot <- get_specific_snapshot("20251130")


```

```{r}

temp_file1 <- tempfile(fileext = ".xlsx")
drive_download(
  file = specific_snapshot$snapshot$id,
  path = temp_file1,
  overwrite = TRUE
)

# Correction to reset back to excel origin
DaysDiff <- as.numeric(as.duration(interval(ymd("1899-12-30"), ymd("1970-01-01"))),"days")


Snapshot <- openxlsx2::wb_to_df(
  temp_file1,
  sheet = "Combined",
  colNames = TRUE,
  detectDates = TRUE
  ) |> mutate(
    PatientID = stringr::str_split_i(TreatmentID,"\\.",1),
     SurgicalTreatment2 = case_when(
       stringr::str_detect(str_to_lower(EBMAComment),"surgery recommended") &
       stringr::str_detect(str_to_lower(SurgicalTreatment), "non") ~ "Surgery recommended",
       stringr::str_detect(str_to_lower(SurgicalTreatment), "non", negate = TRUE) ~ "Surgical",
       stringr::str_detect(str_to_lower(SurgicalTreatment), "non") ~ "Non-Surgical"
  )
  ) |> unite(
  col = "CombID",
  sep = ".",
  c("PatientID","AffectedSide"),
  remove = FALSE
)




STROBEInput <- openxlsx2::wb_to_df(
  temp_file1,
  sheet = "Strobe_Input",
  colNames = TRUE,
  detectDates = TRUE
  )

```

#Snapshot validation

```{r}
# Identify dropped records
dropped_records <- TreatTable |> filter(
  lubridate::ymd(DateTreatmentRecordCreation) <= ymd(CurrentDate)
) |> mutate(
  TreatmentID = as.character(
    TreatmentID
    )
  ) |> anti_join(
      Snapshot, by = "TreatmentID"
      )

# Row count summary
epoxy(
  "TreatTable (live):   {nrow(TreatTable)} records",
  "Snapshot (pipeline): {nrow(Snapshot)} records",
  "Dropped records:     {nrow(dropped_records)} records",
  .sep = "\n"
)
```

```{r}

STROBEInc <- STROBEFlow |> filter(
  !is.na(followup)
)
# Identify dropped records
DroppedKneeIntra <- TreatTable |> filter(
  TreatmentID %in% STROBEInc$followup
) |> mutate(
  TreatmentID = as.character(
    TreatmentID
    )
  ) |> anti_join(
      KneeIntraop, join_by("TreatmentID" == "Treatment ID")
      )

# Row count summary
epoxy(
  "TreatTable (live):   {nrow(TreatTable)} records",
  "KneeIntraop : {nrow(KneeIntraop)} records",
  "Dropped records:     {nrow(DroppedKneeIntra)} records",
  .sep = "\n"
)
```
```{r}


# Identify dropped records
SnapIntrDrop <- KneeIntraop |> filter(
  !is.na(Anaesthetic)
)  |> anti_join(
      Snapshot |> filter(
  Surgeon == "SM",
  SurgicalTreatment2 == "Surgical",
  RegistryCohortName == "KneeArthritis",
), join_by("Treatment ID" == "TreatmentID")
      )

# Row count summary
epoxy(
  "KneeIntraop : {nrow(KneeIntraop)} records",
  "Snapshot (pipeline):   {nrow(Snapshot)} records",
  "Dropped records:     {nrow(SnapIntrDrop)} records",
  .sep = "\n"
)
```

# Context

The Arthroplasty Outcomes in Regional Australia (AORA) registry has been in operation since June 2020, collecting KneeArthritis and HipArthritis presentations to a private clinic in Grafton, NSW. The setup of the registry is detailed on the [registry wiki](https://sites.google.com/ebma.com.au/aora-registry-wiki/home). The registry started with two surgeons contributing with one surgeon stopping participation in December 2022.

# Recruitment Flow

Flowcharts as per STROBE [@Vandenbroucke2007] and RECORD [@Benchimol2015] guidelines were generated for treatments enrolled into the Registry. Followup was set to eligibility at 6months followup.


```{r}

CurrentDate <- as.character("20251130")


STROBEFlow <- STROBEInput |> left_join(
  KneeIntraop |> dplyr::select(
    -Timestamp
  ),
  join_by(TreatmentID == "Treatment ID")
) |> dplyr::left_join(# Join with relevant columns from Snapshot
    Snapshot |> 
      dplyr::select(
        TreatmentID,
        CombID,
        EligibleAtPreop,
        EligibleAtx6months,
        SurgicalTreatment2
      ) |> 
      # Convert all date columns to date format
      dplyr::mutate(
        across(contains("Date"), lubridate::ymd)
      ),
    by = "TreatmentID"
  ) |> dplyr::mutate(
    TreatmentStatus2 = if_else(
          TreatmentStatus == "No further followup" & is.na(DateTreatment),
          "Archived",
          TreatmentStatus
  )
  ) |> dplyr::mutate(
    exclusion1 = case_when(
    RegistryCohortName != "KneeArthritis" ~ "Diagnosis not of interest",
    (SurgicalTreatment2 != "Surgical" | is.na(SurgicalTreatment2) | str_detect(TreatmentStatus,"Pending")) & RegistryCohortName == "KneeArthritis" ~ "Not a surgical treatment",
     SurgicalTreatment2 == "Surgical" & RegistryCohortName == "KneeArthritis" & stringr::str_detect(RegistryStatus,"Opt-out", negate = TRUE) & TreatmentType != "Primary" ~ "Non-primary procedure",
    (SurgicalTreatment2 != "Surgical" | !is.na(SurgicalTreatment2)) & RegistryCohortName == "KneeArthritis" & stringr::str_detect(RegistryStatus,"Opt-out") ~ "Patient Opt-Out",
    SurgicalTreatment2 == "Surgical" & RegistryCohortName == "KneeArthritis" & stringr::str_detect(RegistryStatus,"Opt-out", negate = TRUE) & str_detect(TreatmentStatus,"Pending", negate = TRUE) & TreatmentType == "Primary" & Surgeon != "SM" ~ "Non-participating surgeon",
    .default = NA_character_
  ),
  induction = if_else(
    is.na(exclusion1),
    TreatmentID,
    NA_character_
  ),
exclusion2 = case_when(
  #!is.na(induction) & is.na(Approach) ~ "No data entered",
  !is.na(induction) & !is.na(Approach) & stringr::str_detect(Approach, "vastus", negate = TRUE) ~ "Not approach of interest",
),
followup = if_else(
  is.na(exclusion1) & is.na(exclusion2),
  TreatmentID,
  NA_character_
),
lost_followup = if_else(
  EligibleAtx6months != "Yes",
  "Not eligible for followup",
  NA_character_
),
mitt = if_else(
    !is.na(followup) & is.na(lost_followup),
    TreatmentID,
    NA_character_
)
) |> dplyr::rename(
  trialno = "TreatmentID"
)

```



```{r}
#| label: fig-strobe-cohort1
#| fig-cap: "Flowchart of extraction and followup of surgical sample from the Registry"


STROBEPlot1 <- consort_plot(
  data = STROBEFlow,
 orders = c(
   trialno = "Population",
   exclusion1 = "Ineligible for TKA",
   induction = "Surgical pool",
   exclusion2 = "Excluded",
   followup = "Eligible for analysis",
   lost_followup = "Not eligible for followup",
   mitt = "Followup Analysis"
   ),
 side_box = c(
   "exclusion1",
   "exclusion2",
   "lost_followup"
   ),
 cex = 0.6
)

knitr::knit_print(STROBEPlot1)

```

Cumulative recruitment over time was plotted from Registry inception to the present.

```{r}
#| label: fig-progress
#| fig-cap: "Cumulative cohort recruitment within the registry from inception to present"

target_date <- lubridate::ymd("2022-Nov-02")  # Set your date here

RecordCount <- dplyr::summarise(
  STROBEFlow |>  dplyr::filter(
    !is.na(followup)
    ),
  Count = n(),
  .by = PatientCreationDate
) |> arrange(
  PatientCreationDate
) |> dplyr::mutate(
  CumulativeCount = cumsum(Count),
  PatientCreationNum = as.numeric(PatientCreationDate)
  ) |> filter(
    !(PatientCreationDate < ymd("20160701"))
   
  )

cumulative_plot <- ggplot(RecordCount, aes(x = PatientCreationDate, y = CumulativeCount)) +
  geom_line(color = "#2c3e50", linewidth = 1) +
  # Add the spline fit with confidence interval
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), 
              color = "#e74c3c", linewidth = 1.2, se = TRUE, fill = "#e74c3c", alpha = 0.2) +
  geom_point(color = "#3498db", size = 1) +
  
  geom_vline(xintercept =  target_date,
             linetype = "dashed", color = "#27ae60", linewidth = 0.8) +
  annotate("text", x = target_date, y = Inf,
           label = "Introduction of Flex bearing", vjust = 1.5, hjust = -0.1,
           color = "#27ae60", fontface = "bold", size = 3.5) +
  # Add labels and title
  labs(
    x = "Date",
    y = "Cumulative Number of Cases",
    #caption = "Data source: STROBEFlow3"
  ) +
  # Improve the theme and formatting
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

# Print the plot
knitr::knit_print(cumulative_plot)


```

# Baseline and Demographics

```{r}
SubVasMaster <- Snapshot |> filter(
  TreatmentID %in% STROBEFlow$followup  
) |> left_join(
  IntHistory1 |> dplyr::select(
    TreatmentID,
    EducationLevel:SymptomOnset,
    SymptomDuration1
  ),
  by = "TreatmentID"
) |> left_join(
  MMMPostcode,
  join_by(Postcode == postcode),
  relationship = "many-to-one"
) |> mutate(
  across(
      ComorbHeartDisease_Preop:ComorbOtherMedicalCondition_Preop,
      ~ case_when(
        str_detect(.x, "not") ~ 0,
        str_detect(.x, "not|activities|treatment", negate = TRUE) ~ 1,
        str_detect(.x, "treatment") ~ 2,
        str_detect(.x, "activities")~ 3
      )
    ),
    SACQ_score = if_else(
      rowSums(!is.na(pick(ComorbHeartDisease_Preop:ComorbOtherMedicalCondition_Preop))) == 0L,
      NA_integer_,
      rowSums(
        pick(ComorbHeartDisease_Preop:ComorbOtherMedicalCondition_Preop),
        na.rm = TRUE
    )
    ),
  across(
      MODEMQ1_Preop:MODEMQ6_Preop,
      ~ case_when(
        str_detect(.x, "Extremely") ~ 4,
        str_detect(.x, "Very") ~ 3,
        str_detect(.x, "Somewhat") ~ 2,
        str_detect(.x, "Slightly") ~ 1,
        str_detect(.x, "Not.likely") ~ 0,
        str_detect(.x, "applicable") ~ NA,
        is.na(.x) ~ NA
      )
    ),
    MODEMExp = if_else(
      rowSums(!is.na(pick(MODEMQ1_Preop:MODEMQ6_Preop))) == 0,
      NA_integer_,
      rowSums(
        pick(MODEMQ1_Preop:MODEMQ6_Preop),
        na.rm = TRUE
    )
    )
)


```



```{r}
#| label: tbl-subvas-demographics
#| tbl-cap: "Summary of demographics of subvastus cohort"

Tablesubvasdemo <- gtsummary::tbl_summary(
  SubVasMaster |> dplyr::select(
    AgeAtTreatment,
    Sex,
    EducationLevel,
    mmm_label,
    SACQ_score,
    MODEMExp,
    KOOS12_Pain_TotalScore_Preop,
    VR12_Physical_TotalScore_Preop,
    VR12_Mental_TotalScore_Preop,
    TreatmentStatus,
    DateTreatment
  ),
  #by = "CRTiming",
  missing = "no",
  statistic = list(
    DateTreatment ~ "{min} - {max}"
  )
) 

knitr::knit_print(Tablesubvasdemo)
```

# Complications

```{r}
SubVasComp <- SubVasMaster |> dplyr::select(
  TreatmentID,
  DateTreatment,
  TreatmentStatus,
  TreatmentStatusNotes,
  DateStatusChange,
  ComplicationOccurrence,
  DateOfOccurrence,
  ComplicationNature,
  ReoperationProcedure,
  ReoperationProcedureDate
) |> mutate(
  ComplicationOccur2 = if_else(
    is.na(ComplicationOccurrence),
    "No",
    ComplicationOccurrence
  ),
  OccurDelay =  as.numeric(as.duration(interval(ymd(DateTreatment), ymd(DateOfOccurrence))),"days"),
  Followup = if_else(
    is.na(DateStatusChange),
    as.numeric(as.duration(interval(ymd(DateTreatment), ymd(CurrentDate))),"days"),
    as.numeric(as.duration(interval(ymd(DateTreatment), ymd(DateStatusChange))),"days")
  )
)



```

```{r}
#| label: tbl-comp
#| tbl-cap: "Summary of complications incidence after surgery separated by group"

TableSubVasComp <- gtsummary::tbl_summary(
  SubVasComp |> dplyr::select(
    ComplicationOccur2,
    OccurDelay,
    Followup
  ),
  missing = "no"
) |>
  modify_footnote_body(
    footnote = "Days",
    columns = "label",
    rows = variable == c("OccurDelay","Followup") & row_type == "label"
  ) |> add_overall()

knitr::knit_print(TableSubVasComp)


```

Adverse events were detected in 16% of surgical cases performed by SM over the life of the registry as shown in @tbl-comp, with an average detection with 30 days of surgery.

Write complications table for SM review

```{r}
#| label: write-complic
#| execute: false

# Authenticate for sheets using the same token
gs4_auth(token = drive_token())


# SubVasComp <- googlesheets4::gs4_create(
#   "AORA_SubVasComp",
#   sheets = "Complications"
# )

sheet_write(
  SubVasComp |> dplyr::select(
    -ComplicationOccurrence
  ) |> filter(
    ComplicationOccur2 != "No"
  ),
  ss = "https://docs.google.com/spreadsheets/d/14gEhfKChS-Pbi6wbRRYNaUKO_ooestwRw7YGQLQtJHM?usp=drive_fs",
  sheet = "Complications"
)

```

# Patient reported outcomes


```{r}
SubvKOOSTotal <- SubVasMaster |> reframe(
  Quartile              = c("n", "p25", "p50", "p75"),
  Pain_6wk        = c(sum(!is.na(KOOS12_Pain_TotalScore_6weeks)),          quantile(KOOS12_Pain_TotalScore_6weeks,          c(0.25,0.5,0.75), na.rm = TRUE)),
  ADL_6wk         = c(sum(!is.na(KOOS12_DailyLiving_TotalScore_6weeks)),   quantile(KOOS12_DailyLiving_TotalScore_6weeks,   c(0.25,0.5,0.75), na.rm = TRUE)),
  Quality_6wk     = c(sum(!is.na(KOOS12_Quality_TotalScore_6weeks)),        quantile(KOOS12_Quality_TotalScore_6weeks,        c(0.25,0.5,0.75), na.rm = TRUE)),
  Total_6wk       = c(sum(!is.na(KOOS12_Summary_TotalScore_6weeks)),        quantile(KOOS12_Summary_TotalScore_6weeks,        c(0.25,0.5,0.75), na.rm = TRUE)),
  Pain_6mth       = c(sum(!is.na(KOOS12_Pain_TotalScore_6months)),          quantile(KOOS12_Pain_TotalScore_6months,          c(0.25,0.5,0.75), na.rm = TRUE)),
  ADL_6mth        = c(sum(!is.na(KOOS12_DailyLiving_TotalScore_6months)),   quantile(KOOS12_DailyLiving_TotalScore_6months,   c(0.25,0.5,0.75), na.rm = TRUE)),
  Quality_6mth    = c(sum(!is.na(KOOS12_Quality_TotalScore_6months)),       quantile(KOOS12_Quality_TotalScore_6months,       c(0.25,0.5,0.75), na.rm = TRUE)),
  Total_6mth      = c(sum(!is.na(KOOS12_Summary_TotalScore_6months)),       quantile(KOOS12_Summary_TotalScore_6months,       c(0.25,0.5,0.75), na.rm = TRUE))
)


```

```{r}
#| label: tbl-koos
#| tbl-cap: "Summary of KOOS subscales at 6 weeks and 6months"


SubvKOOSTotal |>
  gt::gt() |>
  cols_label(
    Quartile    = "",
    Pain_6wk    = "Pain",
    ADL_6wk     = "ADL",
    Quality_6wk = "Quality",
    Total_6wk   = "Total",
    Pain_6mth   = "Pain",
    ADL_6mth    = "ADL",
    Quality_6mth = "Quality",
    Total_6mth  = "Total"
  ) |>
  tab_spanner(
    label   = "6 Weeks",
    columns = c(Pain_6wk, ADL_6wk, Quality_6wk, Total_6wk)
  ) |>
  tab_spanner(
    label   = "6 Months",
    columns = c(Pain_6mth, ADL_6mth, Quality_6mth, Total_6mth)
  ) |>
  fmt_number(
    columns  = everything(),
    rows     = Quartile != "n",
    decimals = 1
  ) |>
  fmt_integer(
    columns = everything(),
    rows    = Quartile == "n"
  ) |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_row_groups()
  ) |>
  tab_style(
    style     = cell_borders(sides = "bottom", color = "#d3d3d3", weight = px(1)),
    locations = cells_body(rows = Quartile == "n")
  )

```


```{r}

levelskneel <- SubVasMaster |> distinct(Kneeling_6months)

SVPlotData <- SubVasMaster |> filter(
  !is.na(Kneeling_6months)
) |> mutate(
  Kneeling_6months = str_trim(Kneeling_6months),
  Kneeling_6months = forcats::fct(
    Kneeling_6months,
    levels = c("Extreme","Severe","Moderate","Mild","None")
  )
) |>  count(Kneeling_6months) |> mutate(
  proportion = n / sum(n),
  percentage = round(proportion * 100, 1)
) 

# Create stacked barplot
ggplot(SVPlotData, aes(x = "", y = proportion, fill = Kneeling_6months)) +
  geom_col() +
  geom_text(
    aes(label = paste0(percentage, "%")),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 3.5
  ) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = NULL,
    y = "Proportion",
    fill = "Kneeling difficulty at 6month followup"
  ) +
  theme_minimal()

```







## Monitoring Module

```{r}

MonitorSubVas <- MonitorResponse |> filter(
  TreatmentID %in% SubVasMaster$TreatmentID
) |> group_by(
  TreatmentID
  ) |> arrange(TimeStamp) |> 
  mutate(Sequence = row_number()) |> 
  ungroup() |>
  unite(
    col = "FormID",
    c(TreatmentID,Sequence),
    sep = ".",
    na.rm = FALSE,
    remove = FALSE
  ) |> group_by(
    FormID
  ) |> mutate(
    ResponseCount = n(),
    OutOfSchedule = if_else(
      (DaysAfterSurgery == 8 | DaysAfterSurgery == 10 | DaysAfterSurgery == 12 | DaysAfterSurgery >= 14),
      TRUE,
      FALSE
    ),
    DateStamp = lubridate::as_date(TimeStamp)
  ) |> ungroup() |> arrange(FormID) 

```

```{r}
SubVasPain <- MonitorSubVas |> group_by(TreatmentID) |>
  slice_max(
    WorstPain24,
    n = 1,
    with_ties = FALSE) |> ungroup()

```


```{r}

MonitorPain <- summarise(
  SubVasPain,
  WorstPain_Q1  = quantile(as.numeric(WorstPain24), 0.25, na.rm = TRUE),
  WorstPain_Med = median(as.numeric(WorstPain24), na.rm = TRUE),
  WorstPain_Q3  = quantile(as.numeric(WorstPain24), 0.75, na.rm = TRUE),
  Days_Q1       = quantile(DaysAfterSurgery, 0.25, na.rm = TRUE),
  Days_Med      = median(DaysAfterSurgery, na.rm = TRUE),
  Days_Q3       = quantile(DaysAfterSurgery, 0.75, na.rm = TRUE)
)

```

```{epoxy}
Patients reported a median worst pain score of {MonitorPain$WorstPain_Med} (IQR {MonitorPain$WorstPain_Q1} - {MonitorPain$WorstPain_Q3}) at a median of {MonitorPain$Days_Med} days after surgery (IQR {MonitorPain$Days_Q1} - {MonitorPain$Days_Q3}).
```
